---
title: "first_report"
author: "Peter Tempfli"
date: "9/25/2019"
output: html_document
---

```{r}
library(ggplot2)
library(reshape)
df <- read.csv("~/Desktop/uni/thesis_repo/KVH_data.csv")
months = names(df)[7:18]
df['row_mean'] = apply(df[,months],1,mean)
df$row_mean = sqrt(df$row_mean)
```

# Consumption monthly plot
First, plot monthly consumption for **EVERY UNIT**. We can see some trends, but not really visible. Mostly because the scale is very different.

```{r}
# on map
#ggplot(data=df, aes(x=Lon, y=Lat)) + geom_point()
# monthly consumpltion plot
m = df[,months]
m['id'] = seq(1:220)
m_long <- melt(m, id.vars=c('id'))

ggplot(data=m_long, aes(x=variable, y=value, group=id)) + geom_line()
```

# Normalized monthly plot
On this plot the values normalized by the mean of the unit. This way the values are more comparable so some trends are more visible. We can see that some units has more extreme behavior (steep), while some of them are more smooth.

```{r}
m_ = df[,months]
m_norm_by_mean = m_ / apply(m_, 1, mean)
m_norm_by_mean['id'] = seq(1:220)
m_norm_by_mean_long = melt(m_norm_by_mean[10:70,], id.vars=c('id'))
ggplot(data=m_norm_by_mean_long, aes(x=variable, y=value, group=id)) + geom_line()
```
```{r}
library(leaflet)

pal <- colorNumeric(palette = "inferno", domain = df$row_mean)

mp <- leaflet(data = df) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addCircleMarkers(~Lon, ~Lat, radius = ~row_mean/5, color=~pal(row_mean))
mp
```